Supplementary Content

### 2022-03-14 experiments/2_supplement/supplement.Rmd
Fixes #24

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r echo = FALSE}
run_sims_this_section <- FALSE
```

@@

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(1, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

>>>>

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))

@@

```{r echo = FALSE}
run_sims_this_section <- TRUE
```

@@

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(1, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")

rm(sp)
